QECO: A QoE-Oriented Computation Offloading Algorithm based on Deep Reinforcement Learning for Mobile Edge Computing

### 2024-11-15 Response/Paper_Res.tex
Rev_V8.5

Recall that $y_{i,j}(t)$ is the offloading indicate function. Moreover, among all $j \in \mathcal{J}$, $y_{i,j}=1$ only for one $j$ which is the corresponding EN.
}}
\end{my}\vspace{5mm}

@@

\begin{figure}[H]
	\captionsetup{name=Fig.}
	\centering
	\includegraphics[width=.6\linewidth]{m1}
	\vspace*{-3mm}
	\caption{\textcolor{blue}{The convergence of the average QoE across episodes under different DQN-based methods.}}
	\vspace*{-3mm}
	\label{chart111}
\end{figure}
		\begin{my}{1cm}{1cm}
	\rev{
		{\

@@

\,\,\,\,We finally delve into the investigation of the convergence performance of the QECO algorithm in Fig.~\ref{chart111} and Fig. 8. To validate the effectiveness of the QECO algorithm, we assess its convergence rate compared to the vanilla DQN and DDQN configurations \cite{van2016deep}, measured by the average QoE across episodes. As shown in Fig.~\ref{chart111}, as the episodes progress, the MD's network learns efficient policies, ultimately stabilizing as it approaches convergence. Specifically, the DQN, DDQN, and our proposed QECO algorithm converge after approximately 650, 550, and 450 iterations, respectively. The QECO algorithm demonstrates the faster convergence while achieves a higher average QoE than the other methods. underscore the beneficial impact of workload prediction by the LSTM network and highlight its effectiveness in efficiently utilizing the processing capabilities of  MDs and ENs. \\\dots }}

@@

\begin{figure}[H]
	\captionsetup{name=Fig.}
	\centering
	\includegraphics[width=.6\linewidth]{m1}
	\vspace*{-3mm}
	\caption{\textcolor{blue}{The convergence of the average QoE across episodes under different DQN-based methods.}}
	\vspace*{-3mm}
	\label{chart111}
\end{figure}
\begin{my}{1cm}{1cm}
	\rev{
		{\

			\,\,\,\,We finally delve into the investigation of the convergence performance of the QECO algorithm in Fig.~\ref{chart111} and Fig. 8. To validate the effectiveness of the QECO algorithm, we assess its convergence rate compared to the vanilla DQN and DDQN configurations \cite{van2016deep}, measured by the average QoE across episodes. As shown in Fig.~\ref{chart111}, as the episodes progress, the MD's network learns efficient policies, ultimately stabilizing as it approaches convergence. Specifically, the DQN, DDQN, and our proposed QECO algorithm converge after approximately 650, 550, and 450 iterations, respectively. The QECO algorithm demonstrates the faster convergence while achieves a higher average QoE than the other methods. underscore the beneficial impact of workload prediction by the LSTM network and highlight its effectiveness in efficiently utilizing the processing capabilities of  MDs and ENs. \\\dots }}

>>>>

Recall that $y_{i,j}(t)$ is the binary offloading indicator. Moreover, among all $j \in \mathcal{J}$, $y_{i,j}=1$ only for one $j$ which is the corresponding EN.
}}
\end{my}\vspace{5mm}

@@

\begin{figure}[H]
	\captionsetup{name=Fig.}
	\centering
	\includegraphics[width=.6\linewidth]{m1}
	\vspace*{-3mm}
	\caption{\textcolor{blue}{The convergence of the average QoE across episodes under different DQN-based methods.}}
	\vspace*{-3mm}
	\label{chartC0}
\end{figure}

We have also added the following paragraph in Section V of the revised manuscript to explain the results of the comparison in Fig.~\ref{chartC0}.

@@

\,\,\,\,We finally delve into the investigation of the convergence performance of the QECO algorithm in Fig.~\ref{chartC0} and Fig. 8. To validate the effectiveness of the QECO algorithm, we assess its convergence rate compared to the vanilla DQN and DDQN configurations \cite{van2016deep}, measured by the average QoE across episodes. As shown in Fig.~\ref{chartC0}, as the episodes progress, the MD's network learns efficient policies, ultimately stabilizing as it approaches convergence. Specifically, the DQN, DDQN, and our proposed QECO algorithm converge after approximately 650, 550, and 450 iterations, respectively. The QECO algorithm demonstrates the faster convergence while achieves a higher average QoE than the other methods. underscore the beneficial impact of workload prediction by the LSTM network and highlight its effectiveness in efficiently utilizing the processing capabilities of  MDs and ENs. \\\dots }}

@@

Furthermore, to enhance the evaluation of our work, we have extended the performance analysis by comparing QECO with two baseline schemes, vanilla DQN and DDQN \cite{van2016deep}. This comparison illustrates the impacts of the LSTM network and dueling architecture. We have added Fig.~\ref{chartC1} to Section VI of the revised manuscript.

\begin{figure}[H]
	\captionsetup{name=Fig.}
	\centering
	\includegraphics[width=.6\linewidth]{m1}
	\vspace*{-3mm}
	\caption{\textcolor{blue}{The convergence of the average QoE across episodes under different DQN-based methods.}}
	\vspace*{-3mm}
	\label{chartC1}
\end{figure}

We have also added the following paragraph in Section V of the revised manuscript to explain the results of the comparison in Fig.~\ref{chartC1}.
\begin{my}{1cm}{1cm}
	\rev{
		{\ 
			\dots

			\,\,\,\,We finally delve into the investigation of the convergence performance of the QECO algorithm in Fig.~\ref{chartC1} and Fig. 8. To validate the effectiveness of the QECO algorithm, we assess its convergence rate compared to the vanilla DQN and DDQN configurations \cite{van2016deep}, measured by the average QoE across episodes. As shown in Fig.~\ref{chartC1}, as the episodes progress, the MD's network learns efficient policies, ultimately stabilizing as it approaches convergence. Specifically, the DQN, DDQN, and our proposed QECO algorithm converge after approximately 650, 550, and 450 iterations, respectively. The QECO algorithm demonstrates the faster convergence while achieves a higher average QoE than the other methods. underscore the beneficial impact of workload prediction by the LSTM network and highlight its effectiveness in efficiently utilizing the processing capabilities of  MDs and ENs. \\\dots }}

### 2024-11-15 Revision/Paper_Rev.tex
Rev_V8.5

There are two primary categories of related research in resource management for MEC based on target objectives, single-objective optimization and multi-objective optimization methods, where RL are mainstream optimization techniques.
\subsubsection{Single-Objective Optimization} 
Recent research has extensively explored single-objective optimization in the context of MEC, focusing on optimizing a single objective, such as delay or energy consumption. 
Given the dynamic nature of MEC systems, in \cite{li2022integrated} the authors proposed an integrated optimization framework, which leverages past experience and model knowledge to enable fast and resilient real-time offloading control. 
Li \textit{et al.} in \cite{li2020joint} introduced a DRL-based delay-optimal offloading strategy that employs a DQN to learn offloading decisions autonomously. 
To minimize total delay and reduce mobile vehicle task waiting time, Tang \textit{et al.} in \cite{tang2022double} developed a dynamic offloading model for multiple mobile vehicles, segmenting tasks into sequential subtasks for more precise offloading decisions.
Sun \textit{et al.} in \cite{sun2024hierarchical} explored both computation offloading and service caching problems in MEC. They formulated an optimization problem that aims to minimize the long-term average service delay. They then proposed a hierarchical DRL framework, which effectively handles both problems under heterogeneous resources.
To minimize energy consumption, Munir \textit{et al.} \cite{munir2021multi} developed a semi-distributed approach using a multi-agent RL framework for self-powered MEC. 
Zhou \textit{et al.} in \cite{zhou2021deep} proposed a Q-learning approach, which is an extension of RL to achieve optimal resource allocation strategies and computation offloading.
Wang et al. in \cite{wang2020reinforcement} studied the computation offloading problem in MEC systems within cellular networks, emphasizing mobile awareness. They proposed a joint approach for task offloading and computation allocation, aiming to address the task offloading costs associated with user mobility. 
In \cite{zhao2019deep}, Zhao \textit{et al.} proposed a computation offloading algorithm based on DRL, which addresses the competition for wireless channels to optimize long-term downlink utility.
Dai \textit{et al.} in \cite{dai2020edge} introduced the integration of action refinement into DRL and designed an algorithm based on deep deterministic policy gradient (DDPG) to optimize resource allocation and computation offloading concurrently.

@@

 				\cite{li2022integrated} & Online computation offloading & Minimize computation delay & Actor-critic network & Not consider system energy consumtion \\ \midrule
 				\cite{li2020joint} & Caching and computation offloading & Minimize delay of the whole system &  Multi-agent DQN & Not consider system energy consumtion \\ \midrule
 				\cite{tang2022double}  & Computation offloading & Minimize total delay & DDQN & Not consider system energy consumtion \\ \midrule

@@

 				\cite{liu2021learn}  & Resource allocation and computation offloading & Minimize execution cost  & Multi-agent actor-critic network &  Not consider delay-sensitive tasks \\\midrule
 				\cite{wu2023computation}   & Stochastic game-based resource allocation & Minimize energy consumption and processing delay & Multi-agent RL & Not consider tasks with maximum delay tolerance\\\midrule
 				\cite{zhou2021deep} & Resource allocation and computation offloading & Minimize energy consumption of the entire system & DDQN & Only for a single MEC system model \\\midrule				

@@

 				\cite{wu2024privacy} & Joint power allocation and computation offloading  & Optimization of privacy protection and quality of service.  & Multi-agent actor-critic network& Not take user's demand into consideration \\\midrule

@@

 				\cite{Bolourian-WCL24}  & Energy harvesting  computation offloading & Minimize drop rate and energy consumption.  & DQN & Not consider computation delay  \\\midrule
 				\cite{huang2021deadline}  & Computation offloading & Optimize drop rate and energy consumption & DDPG & Not consider computation delay \\ \midrule
 				\cite{gong2022edge} & Resource allocation and computation offloading & Minimize task computation delay and energy consumption  & DRL & Not take user's demand into consideration\\\midrule
 				\cite{sun2024hierarchical} & Computation offloading and service caching & Minimize average service delay & Hierarchical DRL & Not consider system energy consumtion \\\midrule
 				\cite{wu2023multi}  & Computation offloading & Optimize delay and energy consumption  & Multi-agent PPO&  Not consider tasks with maximum delay tolerance \\\midrule

@@

 				\cite{gao2022large}  & Decentralized computation offloading & Optimize system cost and completion rates  & Multi-agent actor-critic network& Not take user's demand into consideration \\\midrule

@@

We define $z_i(t)$ as the index assigned to the computation task arriving at MD $i \in \mathcal{I}$ in time slot $t \in \mathcal{T}$. Let $\lambda_i(t)$ denote the size of this task in bits. \textcolor{blue}{The size of task \( z_i(t) \) is selected randomly and uniformly from a discrete set \( \Lambda = \{\lambda_1, \lambda_2, \ldots, \lambda_{\theta}\} \), where \( \theta \) represents the number of these values. Note that task sizes are drawn from a discrete set since, in many applications, tasks typically come with predefined sizes,~\cite{wang2020intelligent},~\cite{zhang2019toward},~\cite{allahham2022multi}. We consider $\lambda_i(t) \in \Lambda \cup \{0\}$ to include the case that no task has arrived.} We also denote the task's processing density as $\rho_i(t)$ that indicates the number of CPU cycles required to complete the execution of a unit of the task. Furthermore, we denote the deadline of this task by $\Delta_i(t)$ which is the number of time slots that the task must be completed to avoid being dropped.
%At the beginning of time slot $t \in \mathcal{T}$, if MD $i \in \mathcal{I}$ has a newly arrived task, we define $z_i(t)$ as the unique index assigned to that task. Let $\lambda_i(t)$ be the number of newly arrived bits at the beginning of time slot $t \in \mathcal{T}$. If a new task $z_i(t)$ exists at the start of time slot $t$, then $\lambda_i(t)$ is equal to the size of task $z_i(t)$. Otherwise, $\lambda_i(t) = 0$. We consider $\rho_i(t)$ to represent the processing density of task $z_i(t)$, indicating the number of CPU cycles required to process a unit of the task.

@@

In addition to the energy consumed by EN $j$ for task processing, we also take into account the energy consumed by the MD $i$'s user interface in the standby state while waiting for task completion at the EN $j$. We define $E_{i}^{\text{I}}(t)$ as the energy consumption associated with the user interface of MD $i \in \mathcal{I}$, which is given by
%\begin{alignat}{1}
%	E_{i}^{\text{I}}(t) =  \textcolor{blue}{\sum_{\mathcal{J}}y_{i,j}(t)} D_{i,j}^{\text{E}}(t) p_i^{\text{I}} \tau, %= {\lambda_{i,j}^{\text{E}}(t) \rho_i(t) \over \mathcal{B}_j(t) f_j^{\text{E}}} p_i^{\text{I}},
%	\label{16}
%\end{alignat}
\begin{alignat}{1}
		\textcolor{blue}{E_{i}^{\text{I}}(t) =  \sum_{j \in \mathcal{J}}y_{i,j}(t) D_{i,j}^{\text{E}}(t) p_i^{\text{I}} \tau, }
	\label{16}
\end{alignat}
where $p_i^{\text{I}}$ is the standby energy consumption of MD $i \in \mathcal{I}$.  \textcolor{blue}{Recall that $y_{i,j}(t)$ is the offloading indicate function. Moreover, among all $j \in \mathcal{J}$, $y_{i,j}=1$ only for one $j$ which is the corresponding EN.}

@@

The EN randomly selects a sample collection of experiences from the replay buffer, denoted as $\mathcal{N}$. For each experience $n \in \mathcal{N}$, it calculates the value of $	\hat{Q}^{\text{T}}_{i,n}$. This value represents the QoE in experience $n$ and includes a discounted Q-value of the action anticipated to be taken in the subsequent state of experience $n$, according to the network $\textit{Net}^\text{T}_i$, given by
\begin{alignat}{1}
	\hat{Q}_{i,n}^{\text{T}} = \boldsymbol{q}_i(n) + \gamma Q_i^{\text{T}}(\boldsymbol{s}_i(n+1)), \tilde{\boldsymbol{a}}_n; \theta_i^{\text{T}}),
	\label{29}  
\end{alignat}  
where $\tilde{\boldsymbol{a}}_n$ denotes the optimal action for the state $\boldsymbol{s}_i(n+1)$ based on its highest Q-value under $\textit{Net}_i^{\text{E}}$, as given by:
\begin{alignat}{1}
	\tilde{\boldsymbol{a}}_n = \text{arg} \; \max_{\boldsymbol{a} \in \mathcal{A}} \; Q_i^{\text{E}}(\boldsymbol{s}_i(n+1), \boldsymbol{a}; \theta_i^{\text{E}}).
	\label{30}  
\end{alignat} 
In particular, regarding experience $n$, the target-Q value $\hat{Q}_{i,n}^{\text{T}}$ represents the long-term QoE for action $\boldsymbol{a}_i(n)$ under state $\boldsymbol{s}_i(n)$. This value corresponds to the QoE observed in experience $n$, as well as the approximate expected upcoming QoE. %based on $\textit{Net}_i^{\text{T}}_i$, i.e., $\gamma Q_i^{\text{T}}(\mathcal{S}_i(i+1)), \mathcal{A}_i^{\text{N}}; \theta_i^{\text{T}})$
%Based on the set $\mathcal{N}$, the EN trains the MD's neural network using previous sample experiences. Simultaneously, it updates $\theta^{\text{E}}_i$ in $\textit{Net}_i^{\text{E}}$ and computes vector $\hat{\mathbf{Q}}_i^{\text{T}} = (\hat{Q}^{\text{T}}_{i,n})_{n \in \mathcal{N}}$. The key idea of updating $\textit{Net}_i^{\text{E}}$ is to minimize the disparity in Q-values between $\textit{Net}_i^{\text{E}}$ and $\textit{Net}_i^{\text{T}}$, as indicated by the following loss function:
\textcolor{blue}{Based on the set $\mathcal{N}$, the EN computes the vector $\hat{\mathbf{Q}}_i^{\text{T}} = (\hat{Q}^{\text{T}}_{i,n})_{n \in \mathcal{N}}$ and trains the MD's neural network (steps 11-21 of Algorithm~\ref{alg:cap2}) to update the parameter vector $\theta^{\text{E}}_i$ in $\textit{Net}_i^{\text{E}}$ for the next MD's \textit{UpdateRequest}.} The key idea of updating $\textit{Net}_i^{\text{E}}$ is to minimize the disparity in Q-values between $\textit{Net}_i^{\text{E}}$ and $\textit{Net}_i^{\text{T}}$, as indicated by the following loss function:
\begin{alignat}{1}
	\hspace{-2mm}L(\theta_i^{\text{E}},\hat{\mathbf{Q}}_i^{\text{T}}) = {1 \over |\mathcal{N}| }\hspace{-1mm} \sum\limits_{n \in \mathcal{N}} \bigg(Q_i^{\text{E}}(\boldsymbol{s}_i(n) , \boldsymbol{a}_i(n); \theta_i^{\text{E}} ) -   \hat{Q}^{\text{T}}_{i,n}  \bigg)^2.
	\label{31}  
\end{alignat}  
In every \textit{ReplaceThreshold} iterations, the update of $\textit{Net}_i^{\text{T}}$ will involve duplicating the parameters from $\textit{Net}_i^{\text{E}}$ ($\theta_i^{T} = \theta_i^{E}$). The objective is to consistently update the network parameter $\theta_i^{T}$ in $\textit{Net}_i^{\text{T}}$, which enhances the approximation of the long-term QoE when computing the target Q-values in \eqref{28}.\\

>>>>

There are two primary categories of related research in resource management for MEC based on target objectives, single-objective optimization and multi-objective optimization methods, where RL are mainstream optimization techniques.
\subsubsection{Single-Objective Optimization} 
Recent research has extensively explored single-objective optimization in the context of MEC, focusing on optimizing a single objective, such as delay or energy consumption. 
Given the dynamic nature of MEC systems, in \cite{li2022integrated} the authors proposed an integrated optimization framework, which leverages past experience and model knowledge to enable fast and resilient real-time offloading control. 
%Li \textit{et al.} in \cite{li2020joint} introduced a DRL-based delay-optimal offloading strategy that employs a DQN to learn offloading decisions autonomously. 
To minimize total delay and reduce mobile vehicle task waiting time, Tang \textit{et al.} in \cite{tang2022double} developed a dynamic offloading model for multiple mobile vehicles, segmenting tasks into sequential subtasks for more precise offloading decisions.
Sun \textit{et al.} in \cite{sun2024hierarchical} explored both computation offloading and service caching problems in MEC. They formulated an optimization problem that aims to minimize the long-term average service delay. They then proposed a hierarchical DRL framework, which effectively handles both problems under heterogeneous resources.
To minimize energy consumption, Munir \textit{et al.} \cite{munir2021multi} developed a semi-distributed approach using a multi-agent RL framework for self-powered MEC. 
Zhou \textit{et al.} in \cite{zhou2021deep} proposed a Q-learning approach, which is an extension of RL to achieve optimal resource allocation strategies and computation offloading.
Wang et al. in \cite{wang2020reinforcement} studied the computation offloading problem in MEC systems within cellular networks, emphasizing mobile awareness. They proposed a joint approach for task offloading and computation allocation, aiming to address the task offloading costs associated with user mobility. 
In \cite{zhao2019deep}, Zhao \textit{et al.} proposed a computation offloading algorithm based on DRL, which addresses the competition for wireless channels to optimize long-term downlink utility.
Dai \textit{et al.} in \cite{dai2020edge} introduced the integration of action refinement into DRL and designed an algorithm based on deep deterministic policy gradient (DDPG) to optimize resource allocation and computation offloading concurrently.

@@

 				\cite{li2022integrated} & Online computation offloading & Minimize computation delay & Actor-critic network & Overlooking energy consumtion \\ \midrule
 				\cite{li2020joint} & Caching and computation offloading & Minimize total system delay &  Multi-agent DQN & Not consider system energy consumtion \\ \midrule
 				\cite{tang2022double}  & Computation offloading & Minimize total system delay & DDQN & Not consider system energy consumtion \\ \midrule

@@

 				\cite{liu2021learn}  & Resource allocation and computation offloading & Minimize computation cost  & Multi-agent actor-critic network &  Not consider delay-sensitive tasks \\\midrule
 				\cite{wu2023computation}   & Stochastic game-based resource allocation & Minimize computation delay and energy
consumption & Multi-agent RL & Not consider tasks with maximum delay tolerance\\\midrule
 				\cite{zhou2021deep} & Resource allocation and computation offloading & Minimize total energy consumption & DDQN & Limited to a single edge server \\\midrule				

@@

 				\cite{wu2024privacy} & Joint power allocation and computation offloading  & Optimize quality of service  & Multi-agent actor-critic network& Not take user's demand into consideration \\\midrule

@@

 				\cite{Bolourian-WCL24}  & Energy harvesting  computation offloading & Minimize drop rate and energy consumption.  & DQN & Does not account for computation delay  \\\midrule
 				\cite{huang2021deadline}  & Computation offloading & Minimize drop rate and energy consumption & DDPG & Not consider computation delay \\ \midrule
 				\cite{gong2022edge} & Resource allocation and computation offloading & Minimize computation delay and energy
consumption & DRL & Not take user's demand into consideration\\\midrule
 				\cite{sun2024hierarchical} & Computation offloading and service caching & Minimize average delay & Hierarchical DRL & Not consider system energy consumtion \\\midrule
 				\cite{wu2023multi}  & Computation offloading & Minimize computation delay and energy
consumption  & Multi-agent PPO&  Not consider tasks with maximum delay tolerance \\\midrule

@@

 				\cite{gao2022large}  & Decentralized computation offloading & Optimize system cost and computation rates  & Multi-agent actor-critic network& Not take user's demand into consideration \\\midrule

@@

We define $z_i(t)$ as the index assigned to the computation task arriving at MD $i \in \mathcal{I}$ in time slot $t \in \mathcal{T}$. Let $\lambda_i(t)$ denote the size of this task in bits. \textcolor{red}{The size of task \( z_i(t) \) is selected randomly and uniformly from a discrete set \( \Lambda = \{\lambda_1, \lambda_2, \ldots, \lambda_{\theta}\} \), where \( \theta \) represents the number of these values. Note that task sizes are drawn from a discrete set since, in many applications, tasks typically come with predefined sizes,~\cite{wang2020intelligent},~\cite{zhang2019toward}. We consider $\lambda_i(t) \in \Lambda \cup \{0\}$ to include the case that no task has arrived.} We also denote the task's processing density as $\rho_i(t)$ that indicates the number of CPU cycles required to complete the execution of a unit of the task. Furthermore, we denote the deadline of this task by $\Delta_i(t)$ which is the number of time slots that the task must be completed to avoid being dropped.
%At the beginning of time slot $t \in \mathcal{T}$, if MD $i \in \mathcal{I}$ has a newly arrived task, we define $z_i(t)$ as the unique index assigned to that task. Let $\lambda_i(t)$ be the number of newly arrived bits at the beginning of time slot $t \in \mathcal{T}$. If a new task $z_i(t)$ exists at the start of time slot $t$, then $\lambda_i(t)$ is equal to the size of task $z_i(t)$. Otherwise, $\lambda_i(t) = 0$. We consider $\rho_i(t)$ to represent the processing density of task $z_i(t)$, indicating the number of CPU cycles required to process a unit of the task.

@@

In addition to the energy consumed by EN $j$ for task processing, we also take into account the energy consumed by the MD $i$'s user interface in the standby state while waiting for task completion at the EN $j$. We define $E_{i}^{\text{I}}(t)$ as the energy consumption associated with the user interface of MD $i \in \mathcal{I}$, which is given by
%\begin{alignat}{1}
%	E_{i}^{\text{I}}(t) =  \textcolor{blue}{\sum_{\mathcal{J}}y_{i,j}(t)} D_{i,j}^{\text{E}}(t) p_i^{\text{I}} \tau, %= {\lambda_{i,j}^{\text{E}}(t) \rho_i(t) \over \mathcal{B}_j(t) f_j^{\text{E}}} p_i^{\text{I}},
%	\label{16}
%\end{alignat}
\begin{alignat}{1}
		\textcolor{blue}{E_{i}^{\text{I}}(t) =  \sum_{j \in \mathcal{J}}y_{i,j}(t) D_{i,j}^{\text{E}}(t) p_i^{\text{I}} \tau, }
	\label{16}
\end{alignat}
where $p_i^{\text{I}}$ is the standby energy consumption of MD $i \in \mathcal{I}$.  
\textcolor{red}{Recall that $y_{i,j}(t)$ is the binary offloading indicator. Moreover, among all $j \in \mathcal{J}$, $y_{i,j}=1$ only for one $j$ which is the corresponding EN.}

@@

The EN randomly selects a sample collection of experiences from the replay buffer, denoted as $\mathcal{N}$. For each experience $n \in \mathcal{N}$, it calculates the value of $	\hat{Q}^{\text{T}}_{i,n}$. This value represents the QoE in experience $n$ and includes a discounted Q-value of the action anticipated to be taken in the subsequent state of experience $n$, according to the network $\textit{Net}^\text{T}_i$, given by
\begin{alignat}{1}
	\hat{Q}_{i,n}^{\text{T}} = \boldsymbol{q}_i(n) + \gamma Q_i^{\text{T}}(\boldsymbol{s}_i(n+1)), \tilde{\boldsymbol{a}}_n; \theta_i^{\text{T}}),
	\label{29}  
\end{alignat}  
where $\tilde{\boldsymbol{a}}_n$ denotes the optimal action for the state $\boldsymbol{s}_i(n+1)$ based on its highest Q-value under $\textit{Net}_i^{\text{E}}$, as given by:
\begin{alignat}{1}
	\tilde{\boldsymbol{a}}_n = \text{arg} \; \max_{\boldsymbol{a} \in \mathcal{A}} \; Q_i^{\text{E}}(\boldsymbol{s}_i(n+1), \boldsymbol{a}; \theta_i^{\text{E}}).
	\label{30}  
\end{alignat} 
In particular, regarding experience $n$, the target-Q value $\hat{Q}_{i,n}^{\text{T}}$ represents the long-term QoE for action $\boldsymbol{a}_i(n)$ under state $\boldsymbol{s}_i(n)$. This value corresponds to the QoE observed in experience $n$, as well as the approximate expected upcoming QoE. %based on $\textit{Net}_i^{\text{T}}_i$, i.e., $\gamma Q_i^{\text{T}}(\mathcal{S}_i(i+1)), \mathcal{A}_i^{\text{N}}; \theta_i^{\text{T}})$
%Based on the set $\mathcal{N}$, the EN trains the MD's neural network using previous sample experiences. Simultaneously, it updates $\theta^{\text{E}}_i$ in $\textit{Net}_i^{\text{E}}$ and computes vector $\hat{\mathbf{Q}}_i^{\text{T}} = (\hat{Q}^{\text{T}}_{i,n})_{n \in \mathcal{N}}$. The key idea of updating $\textit{Net}_i^{\text{E}}$ is to minimize the disparity in Q-values between $\textit{Net}_i^{\text{E}}$ and $\textit{Net}_i^{\text{T}}$, as indicated by the following loss function:
\textcolor{red}{Based on the set $\mathcal{N}$, the EN computes the vector $\hat{\mathbf{Q}}_i^{\text{T}} = (\hat{Q}^{\text{T}}_{i,n})_{n \in \mathcal{N}}$ and trains the MD's neural network (Lines 11-21 of Algorithm~\ref{alg:cap2}) to update the parameter vector $\theta^{\text{E}}_i$ in $\textit{Net}_i^{\text{E}}$ for the next MD's \textit{UpdateRequest}.} The key idea of updating $\textit{Net}_i^{\text{E}}$ is to minimize the disparity in Q-values between $\textit{Net}_i^{\text{E}}$ and $\textit{Net}_i^{\text{T}}$, as indicated by the following loss function:
\begin{alignat}{1}
	\hspace{-2mm}L(\theta_i^{\text{E}},\hat{\mathbf{Q}}_i^{\text{T}}) = {1 \over |\mathcal{N}| }\hspace{-1mm} \sum\limits_{n \in \mathcal{N}} \bigg(Q_i^{\text{E}}(\boldsymbol{s}_i(n) , \boldsymbol{a}_i(n); \theta_i^{\text{E}} ) -   \hat{Q}^{\text{T}}_{i,n}  \bigg)^2.
	\label{31}  
\end{alignat}  
In every \textit{ReplaceThreshold} iterations, the update of $\textit{Net}_i^{\text{T}}$ will involve duplicating the parameters from $\textit{Net}_i^{\text{E}}$ ($\theta_i^{T} = \theta_i^{E}$). The objective is to consistently update the network parameter $\theta_i^{T}$ in $\textit{Net}_i^{\text{T}}$, which enhances the approximation of the long-term QoE when computing the target Q-values in \eqref{28}.\\
